Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2020-12-23 GWLDCII.tex
as we discuss

In the above work and elsewhere, it is clear that while the space parametrized by the Wilson loop diagrams is related to the Amplituhedron, they are not the same space. For instance, it is conjectured that the Amplituhedron is orientable, whereas Agarwala and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams as a subspace of $\Gr(k, n+1)$ can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$. Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, which can be seen by comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}. This is an intriguing observation, as it is conjectured that the space parametrized by the Wilson loop diagrams will project down to something close to the Amplituhedron \cite{wilsonloop, Amplituhedronsquared}.

The Amplituhedron and the Wilson loop diagrams describe the same physical amplitudes, and via their relation to positroids, they have similar combinatorics, but these combinatorial objects manifest themselves differently in the two cases.  For instance, square moves and merge-expand moves on the plabic graph give different graphical representations of the same positroid cell in the Amplituhedron case, while as we show in our companion paper \cite{generalcombinatoricsI}, retriangulations of polygon dissections associated to Wilson loop diagrams give all the Wilson loop diagrams associated to the same positroid cell.
A direct connection between the geometry of the Amplituhedron and the geometry of the Wilson loop diagrams is also not known.  The geometric spaces in the two situations have different dimensions and \hlfix{examples show}{is this true?} that they do not relate by a coordinate projection or boundary map or other straightforward connection.  The deeper connection, which physics tells us should exist, remains to be uncovered in future work.
\note{This doesn't address the parametrization part yet.}

@@

This paper continues this body of work by establishing concrete connections between the combinatorics of the Wilson loop diagram as determined by the physics, and the combinatorics of the associated positroid cell as identified in \cite{wilsonloop}. In this paper, we give an algorithm to read the Grassmann necklace, one of the standard combinatorial characterizations of the positroid cell, directly off the Wilson loop diagram. We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}. In \cite{non-orientable} the authors note that the Wilson loop diagrams only correspond to positroid cells when the gauge vector is ignored. Including the gauge vector defines a $4k$ dimensional subspace of $\mathbb{G}r_\R(k,n+1)$.\st{This apparent contradiction}\todo{I think we should say more in view of reviewer Y's comment 3 and we can probably phrase it more positively too} \st{is resolved by the non-orientability result of {\cite{non-orientable}}.}

>>>>

In the above work and elsewhere, it is clear that while the space parametrized by the Wilson loop diagrams is related to the Amplituhedron, they are not the same space, nor is a direct connection between the geometry of the Amplituhedron and the geometry of the Wilson loop diagrams known. For instance, it is conjectured that the Amplituhedron is orientable, whereas Agarwala and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams as a subspace of $\Gr(k, n+1)$ can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$. Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, which can be seen by comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}. Furthermore, the spaces in the two situations have different dimensions, as we will discuss further below, and examples show\cite{HeslopSteward} that they do not relate by a coordinate projection or boundary map or other straightforward function.  None the less, from their common physical origin, it is believed that once the integrals over these spaces are taken the resulting amplitudes will show a more direct relation \cite{wilsonloop, Amplituhedronsquared}.

The Amplituhedron and the Wilson loop diagrams describe the scattering amplitudes from the same physical theory, but the Amplituhedron only captures the on-shell portion while the Wilson loop diagrams capture arbitrary kinematics.   Both are related to positroids, and in this way they have similar combinatorics, but, these combinatorial objects manifest themselves differently in the two cases.  For instance, square moves and merge-expand moves on the plabic graph give different graphical representations, hence parametrizations, of the same positroid cell in the Amplituhedron case.  On the other hand, we show in our companion paper \cite{generalcombinatoricsI}, retriangulations of polygon dissections associated to Wilson loop diagrams give all the Wilson loop diagrams associated to the same positroid cell.  Each distinct Wilson loop diagram associated to the same positroid cell gives a different parametrization \cite{WLDdim}. % Despite their common representation as positroids,a direct connection between the geometry of the Amplituhedron and the geometry of the Wilson loop diagrams is not known.  The geometric spaces in the two situations have different dimensions, as we will discuss further below, and examples show\cite{HeslopSteward} that they do not relate by a coordinate projection or boundary map or other straightforward function.
The deeper combinatorial and geometric connection between the Amplituhedron and the Wilson loop diagrams, which physics tells us should exist, remains to be uncovered in future work.

@@

This paper continues the program of establishing concrete connections between the combinatorics of the Wilson loop diagram as determined by the physics, and the combinatorics of the associated positroid cell as identified in \cite{wilsonloop}. In this paper, we give an algorithm to read the Grassmann necklace, one of the standard combinatorial characterizations of the positroid cell, directly off the Wilson loop diagram. We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}. In \cite{non-orientable} the authors note that the Wilson loop diagrams only correspond to positroid cells when the gauge vector is ignored. Including the gauge vector defines a $4k$ dimensional subspace of $\mathbb{G}r_\R(k,n+1)$.\st{This apparent contradiction}\todo{I think we should say more in view of reviewer Y's comment 3 and we can probably phrase it more positively too} \st{is resolved by the non-orientability result of {\cite{non-orientable}}.}
